Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-22 main.tex
Some nits

@@

(Lockstep-)Noninterference is the contoured lockstep hyperproperty
where:
\begin{itemize}
\item For each pair of traces in the hyperproperty, all the contours
  coincide.\apt{This is still a bit ambiguous. How about: For each pair of
    contoured traces in the hyperproperty, the contour is invariant 
    along each trace.}
  \item For each pair of contoured traces in the hyperproperty, if the
    initial elements of the traces are variants, then the observervations
    of the two traces coincide.
\end{itemize}

@@

Generalizing to allow for contours to change throughout the execution,
nested lockstep noninterference is the contoured lockstep hyperproperty
where: \bcp{Which parts of this are common to {\em all} contoured lockstep
  hyperproperties (i.e., which should be part of the definition of contoured
  lockstep hyperproperties) and which are specific to (nested) NI?}
\leo{I'd say contoured lockstep hyperproperties are as above - and the following are
  the generalization for nested ones.}

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, and for every $0 \leq i < n$, there exists in
  the set a pair of traces $\overline{(C', N)}_m$ and $\overline{(C',
    N')}_m$ such that $C_0' = C_i$, $N_0 = M_i$, and $N_0' = M_i'$.
  \apt{I don't see how we can leave $m$ unspecified: doesn't it need to be as long as possible subject to well-formedness? Also, the evolution of $C$ is not determined by the machine, so don't we need $C_j' = C_{i+j}$ for all $0 \leq j < m$ ? }

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, and for every machine state $N_0$ such that
  $N_0$ is a variant of $M_0$, there exists in the set a pair of
  traces $\overline{(C, M)}_m$ and $\overline{(C, N)}_m$.\apt{Same complaint about $n$. And again, $N_0$ defines $\overline{N}$ but it doesn't define $\overline{(C,N)}$. }

\item {\em contour-wellformedness:}

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, $C_0 \leq C_i$ for all $i<n$, where $C \leq
  C'$ if $\forall \component, C(\component) \leq C'(\component)$ and
  $\VIS < \HID$.
  \apt{Isn't this effectively still a negation in the functor? I thought for strategy for describing execution after a Return was to apply suffix closure to the original full trace -- but doesn't this criterion rule out the original full trace?}

>>>>

Finally, we can parameterize the traces by some initial
application-specific state to obtain a {\em contoured lockstep
  $X$-hyperproperty}, where every trace comes with more information.
\leo{Example, call sites in stack safety}

@@

\leo{For this the X- component is empty right?}
Lockstep-Noninterference is the contoured lockstep hyperproperty
where:
\begin{itemize}
\item For each pair of contoured traces in the hyperproperty, the
  contour is invariant along each trace.
\item For each pair of contoured traces in the hyperproperty, if the
  initial elements of the traces are variants, then the observervations
  of the two traces coincide.
\end{itemize}

@@

Lockstep-Noninterference is a restricted form of traditional
noninterference, that is nevertheless useful (e.g. to encode taint
tracking in Section~\leo{Blah}) and easy to test (\leo{More blah}).
At the same time, lockstepness makes it possible to generalize the
setting and allow for the contours themselves to change throughout the
execution.

%Generalizing to allow for contours to change throughout the execution,
%nested lockstep noninterference is the contoured lockstep hyperproperty
%where: \bcp{Which parts of this are common to {\em all} contoured lockstep
%  hyperproperties (i.e., which should be part of the definition of contoured
%  lockstep hyperproperties) and which are specific to (nested) NI?}
%\leo{I'd say contoured lockstep hyperproperties are as above - and the following are
%  the generalization for nested ones.}

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, and for every $0 \leq i < n$, there exists in
  the set a pair of traces $\overline{(C', N)}_m$ and $\overline{(C',
    N')}_m$ such that for all $0 \leq j < m$, $C_j' = C_{i+j}$, $N_0 =
  M_i$, and $N_0' = M_i'$, and where $m$ is the maximum index for
  which $C_i \leq C_{i+j}$ for all $0 \leq j < m$. Here $C \leq C'$ if
  $\forall \component, C(\component) \leq C'(\component)$ and $\VIS <
  \HID$.

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, and for every machine state $N_0$ such that
  $N_0$ is a variant of $M_0$, there exists in the set a pair of
  traces $\overline{(C, M)}_n$ and $\overline{(C, N)}_n$.\apt{Same
    complaint about $n$. And again, $N_0$ defines $\overline{N}$ but
    it doesn't define $\overline{(C,N)}$. }\leo{Cs should be the same
    right?}
